---
title: "Wrangle CEF data"
output: html_notebook
---

```{r setup, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA)
library(tidyverse)
library(tidyquant)
library(readxl)
```

### Get CEF tickers from the spreadsheet

For shiny, the user will tell us the ticker, or name of the fund

```{r}
cef_jkr <- 
  read_excel("Data/CEFList.xlsx", sheet = "FundList")


```

### Import price data, calculate returns, and navs, save as one tibble

```{r}

start_date <- "2010-01-01"

cef_mkt <- 
    tq_get(cef_jkr$Ticker,
           get = "stock.prices",
          from = start_date) %>% 
    dplyr::select(Ticker = symbol, date, close, adjusted, volume) %>% 
    filter(adjusted != "NA") %>% 
    mutate(date = ymd(date)) %>% 
    left_join(cef_jkr, by = "Ticker") %>% 
    dplyr::select(Name, Ticker, date, close, adjusted, volume) %>% 
    group_by(Name)
# 
# afb_mkt <- 
#     tq_get("AFB",
#            get = "stock.prices",
#           from = start_date) %>% 
#     dplyr::select(date, close, adjusted, volume) %>% 
#     filter(adjusted != "NA") %>% 
#     mutate(date = ymd(date)) %>% 
#   add_column(Name = cef_jkr$Name[1], Ticker = "AFB", .before = 1)
#     dplyr::select(Name, Ticker, date, close, adjusted, volume) %>% 
#     group_by(Name)

cef_navs <- 
    tq_get(cef_jkr$NAVTicker,
           get = "stock.prices",
           from = start_date) %>% 
    dplyr::select(NAVTicker = symbol, date, close, adjusted) %>% 
    filter(adjusted != "NA")  %>% 
    mutate(date = ymd(date)) %>% 
    left_join(cef_jkr, by = "NAVTicker") %>% 
    dplyr::select(Name, NAVTicker, date, close, adjusted)  %>% 
    group_by(Name)
  
# create a tibble to hold cef close and cef nav
# add log returns and a premium which is mkt close/ nav close
cef_merged_data <- 
    merge(cef_navs, cef_mkt,
              by = c("Name", "date"),
              suffix = c("_nav", "_mkt"),
              all = TRUE) %>%
    as_tibble() %>% 
    group_by(Name) %>%
    mutate(premium = 100 * (close_mkt / close_nav - 1),
           return_mkt = (log(adjusted_mkt) - log(lag(adjusted_mkt))),
           return_nav = (log(adjusted_nav) - log(lag(adjusted_nav)))) %>%
    dplyr::select(Name, date, premium, Ticker, 
                  close_mkt, adjusted_mkt, return_mkt, volume, 
                  NAVTicker, close_nav, adjusted_nav, return_nav)

save(cef_merged_data, file = "cef_merged_data.Rdata")
```

What is the premium/discount? It's the extent to which the closing price of the CEF is above (premium) or below (discount) the closing price of the NAV CEF. They should be the same. 

### Get mutual fund data

```{r}
mf_tickers <- tribble(
    ~Name, ~Ticker,
    "Vanguard Interm Term Tax Exempt Adm Fd", "VWIUX", 
    "DFA Muni Bd Port Inst", "DFMPX",
    "Vanguard Limited Term Tax Exempt Inv Sh", "VMLTX"
)

mf_prices_returns <- 
    tq_get(mf_tickers$Ticker,
           get = "stock.prices", 
           from = start_date) %>%
    dplyr::select(Ticker = symbol, date, adjusted) %>%
    left_join(mf_tickers, by = "Ticker") %>%  
    mutate(return = log(adjusted) - log(lag(adjusted))) %>% 
    dplyr::select(Name, date, return, Ticker, adjusted)
```

### Choose one closed end fund and one mutual fund for comparison

```{r}
afb <- 
  cef_merged_data %>% 
    filter(Ticker == "AFB") %>%
    filter(return_nav != "NA") %>%
    select(Ticker, date, return_nav, premium)

vwiux <- 
  mf_prices_returns %>%
    filter(Ticker == "VWIUX") %>%
    filter(return != "NA") %>%
    select(Ticker, date, return)
```

### Create rolling cumreturn and correlation functions

```{r}
library(tibbletime)

cumret <- function(data){
    prod(1 + data, na.rm = TRUE) - 1
}

# create rolling functions
# cor_rollified_30 <-  rollify(~cor(.x, .y), window = 30)
cum_ret_rollified <- rollify(cumret, window = 5)
cor_rollified_25 <-  rollify(~cor(.x, .y), window = 25)
```
 
### Apply the rolling functions to one cef and one mutual fund

```{r}
afb_vwiux_combined <- 
  inner_join(afb, vwiux, by = "date", suffix = c("_afb","_vwiux")) %>% 
  rename(return_vwiux = return) %>% 
  as_tbl_time(index = date) %>%
  mutate(return_nav_week = cum_ret_rollified(return_nav),
         return_vwiux_week = cum_ret_rollified(return_vwiux),
         cor_week = cor_rollified_25(return_nav_week, return_vwiux_week))
```

### Apply the rolling functions to all cefs and one mutual fund

```{r}

cef_all <- 
  cef_merged_data %>% 
    filter(return_nav != "NA") %>%
    select(Ticker, date, return_nav, premium)

# create a tibble to hold data for all cefs and vwiux
cefs_all_vwiux <- 
  inner_join(cef_all, vwiux, by = "date", suffix = c("_cef","_vwiux")) %>% 
  rename(return_vwiux = return) %>% 
  as_tbl_time(index = date) %>%
  mutate(return_nav_week = cum_ret_rollified(return_nav),
         return_vwiux_week = cum_ret_rollified(return_vwiux),
         cor_week = cor_rollified_25(return_nav_week, return_vwiux_week))
```

### Run rolling regression of all cefs on the chosen mutual fund

```{r}
# Rex's function, slightly altered, same output
# calculate regression and extract custom values
lmcust <- function(x, y){
    temp <- (lm(x ~ y))
    return(c(coef(temp), 
             summary(temp)$adj.r.squared, 
             sd(temp$residuals)*sqrt(252/5), 
             mean(abs(temp$residuals))
             ))
}


# Make Rex's rolling with rollify
lm_cust_rollified <- rollify(lmcust, 
                        window = 25, 
                        unlist = FALSE)

# the following code flow will run the custom rolling lm of all cefs on the chosen mutual fund
# might take a few seconds to run
cef_vwiux_lm_custom_roll <- 
  cefs_all_vwiux %>% 
  mutate(rolling_model = 
           lm_cust_rollified(return_vwiux_week, 
                      return_nav_week)) %>%
  slice(-1:-24) %>%
  # the next two lines look complicated but it's just reorganizing results, no new calculations
  mutate(r = map(rolling_model, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-rolling_model) %>% 
  rename(intercept = X.Intercept., 
         slope = y, 
         AdjR2 = V3, 
         ResidTE = V4,
         ResidMAD = V5 ) %>% 
  mutate(pred_vwiux_week = lag(intercept) + lag(slope) * return_nav_week,
         err_week = pred_vwiux_week - return_vwiux_week)
```

### JKR addition from tidy world

Let's run a rolling regression that is not customized, using `rollify` and `lm`. Then we can use `tidy` and `glance` to store the results, then `nest` to make the data more compact. This is very similar to the above, except it doesn't extract custom values. It extracts full model results and saves as list columns

```{r}
# Simple regression rolling
lm_rollified <- rollify(~lm(.x ~ .y), 
                        window = 25, 
                        unlist = FALSE)

library(broom)
cef_vwiux_lm_roll <- 
  cefs_all_vwiux %>% 
  mutate(rolling_model = 
           lm_rollified(return_vwiux_week, 
                      return_nav_week)) %>%
  slice(-1:-24) %>%
  mutate(tidied = map(rolling_model,
                      tidy),
         glanced = map(rolling_model,
                       glance)) %>% 
  select(-rolling_model) %>% 
  nest(-Name)

cef_vwiux_lm_roll
```

Question to Rex: I didn't quite understand what was going on in the `justweeks` flow in the code chunk below. 
```{r}    

justweeks <- comb[seq(nrow(comb)%%5, to=nrow(comb), by=5),] %>%
    filter(!is.na(return.nav.week)) %>%
    filter(!is.na(return.mf.week)) %>%
    filter(!is.na(pred.mf.week))

temp <- justweeks %>% 
    tq_mutate(mutate_fun = rollapply,
          select = c(return.nav, return.mf),
          width = 126,
          FUN = cor,
          by.column = FALSE,
          col_rename = c("ok2del1", "cor.week2", "ok2del2", "ok2del3")) %>%
    select(-starts_with("ok2del"))

lm_daily <- lm(return.mf ~ return.nav, data=comb[comb$date>"2018-01-08",])
lm_weekly <- lm(return.mf.week ~ return.nav.week, data=justweeks[justweeks$date>"2018-01-08",])
summary(lm_daily)
summary(lm_weekly)

sd(comb$return.mf[comb$date>"2018-01-08"])
sd(comb$return.nav[comb$date>"2018-01-08"])
sd(comb$return.mf[comb$date>"2018-01-08"]) / sd(comb$return.nav[comb$date>"2018-01-08"])
sd(justweeks$return.mf.week[justweeks$date>"2018-01-08"])
sd(justweeks$return.nav.week[justweeks$date>"2018-01-08"])
sd(justweeks$return.mf.week[justweeks$date>"2018-01-08"]) / sd(justweeks$return.nav.week[justweeks$date>"2018-01-08"])

sd(test2$err.mf.week, na.rm = TRUE)*sqrt(252/5)   
mean(abs(test2$err.mf.week)-mean(test2$err.mf.week, na.rm=TRUE), na.rm = TRUE)

```







